\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{xcolor}
\usepackage{hyperref}
\definecolor{medium}{RGB}{0,171,108}
\hypersetup{
    colorlinks=true, linkcolor=medium,
    filecolor=magenta, urlcolor=cyan,
    pdftitle={Notes}, bookmarks=true,
    pdfauthor={Medet Can Akuş}
}
\urlstyle{same}
\title{Notes}
\author{Medet Can Akuş}
\date{\today}

\begin{document}
\tableofcontents
\maketitle
\section{Notes}
 \begin{itemize}
    \item By default all rust crates link to standard library, which depends on the operating system for features such as \
    threads, scheduling, file, or networking. It also include \hyperlink{ref:libc}{libc} library. 
    \item We can disable inclusion of standard library in rust through the \hyperlink{ref:attribute}{no\_std} attribute.
    \item Cargo.toml file in a rust project contains project configurations such as dependencies, author, version etc...
    \item Panic handler function is part of the standard library and it defines the function that the compiler should invoke when \hyperlink{ref:panic}{panic} occurs. Panic handler is a divergent function.
    \item Rust has a special syntax for \hyperlink{ref:diverging-function}{diverging functions} which are functions that do not return;
    \item \hyperlink{ref:language-item}{Language items} are special functions and types that are internally required by compiler.
    \item When you run a rust application first thing that gets executed is not your main function, it is a function that named start.
    The reason for that because \hyperlink{ref:runtime-environment}{runtime environment} needs be set up and exists before your main application. This environment creates the stack places the right arguments 
    on to the register.
 \end{itemize}
 \section{References}
 \begin{itemize}
    \item \hypertarget{ref:libc}{\textbf{\color{medium}{libc}}}
    \begin{itemize}
        \item \url{https://www.gnu.org/software/libc/}
    \end{itemize}
    \item \hypertarget{ref:attribute}{\textbf{\color{medium}{attribute}}}
    \begin{itemize}
        \item \url{https://doc.rust-lang.org/rust-by-example/attribute.html}
    \end{itemize}
    \item \hypertarget{ref:panic}{\textbf{\color{medium}{panic}}}
    \begin{itemize}
        \item \url{https://doc.rust-lang.org/stable/book/ch09-01-unrecoverable-errors-with-panic.html}
    \end{itemize}
    \item \hypertarget{ref:diverging-function}{\textbf{\color{medium}{Diverging Function}}}
    \begin{itemize}
        \item \url{https://doc.rust-lang.org/1.30.0/book/first-edition/functions.html#diverging-functions}
    \end{itemize}
    \item \hypertarget{ref:language-item}{\textbf{\color{medium}{Language Items}}}
    \begin{itemize}
        \item \url{https://manishearth.github.io/blog/2017/01/11/rust-tidbits-what-is-a-lang-item/}
        \item \url{https://doc.rust-lang.org/1.5.0/reference.html#language-items}
        \item \url{https://doc.rust-lang.org/1.5.0/book/lang-items.html}
    \end{itemize}
    \item \hypertarget{ref:runtime-environment}{\textbf{\color{medium}{Runtime Environment}}}
    \begin{itemize}
        \item \url{https://en.wikipedia.org/wiki/Runtime_system}
    \end{itemize}
    \item \hypertarget{ref:non}{\textbf{\color{medium}{ABI}}}
    \begin{itemize}
        \item \url{https://en.wikipedia.org/wiki/Application_binary_interface}
    \end{itemize}
    \item \hypertarget{ref:non}{\textbf{\color{medium}{Cross Compiler}}}
    \begin{itemize}
        \item \url{https://en.wikipedia.org/wiki/Cross_compiler}
    \end{itemize}
 \end{itemize}
\end{document}